\section{AV Overview}
\subsection{Security principles}
    Computer security is strictly linked to information security, due  to  its  core  nature:  data. AV, to perform the right decision, has to analyze data taken from sensors, and this make them premium targets of malicious attackers. As a defending mechanism, information security principles should be applied to AV. The three core 
    principles should be achieved:
    \begin{itemize}
        \item confidentiality, for prevent an unauthorized access to data;
        
        \item integrity, for detect an unauthorized access to data and prevent an unauthorized modification to data;
        
        \item availability, for the capability to correctly work all the time.
    \end{itemize}
    Privacy, authenticity, accountability, non-repudiation and reliability are additional properties that AV security might aim to achieve, depending on specific requirements.

\subsection{AV Variety}
    As mentioned before, AV have different level of automation. National Highway Traffic Safety Administration (NHTSA) [9] classifies vehicle automation in six levels:
    
    \begin{itemize}
        \item \textit{No-Automation (Level 0)}At all times, the driver has complete and sole command and control of the vehicle with respect to steering, braking, throttle and motive power;

        \item \textit{Driver Assistance (Level 1)} vehicle is controlled by the driver, but some driving assist features may be included in the vehicle design;
        
        \item \textit{Partial Automation (Level 2)} Vehicle has combined automated functions but the driver must remain engaged with the driving tasks;

        
        \item \textit{Conditional Automation (Level 3)} Driver is necessity, but is not required to monitor the environment. The driver must be ready to take control of the vehicle at all times with notice;

        
        \item \textit{High Automation (Level 4)} The vehicle is capable of performing all driving functions. The driver may have the option to control the vehicle;
        
        \item \textit{Full self-Driving automation (Level 5)} The vehicle is intelligently designed to monitor roadway conditions and act solo, performing all safety–critical driving functions for an entire trip.

    \end{itemize}

\subsection{Challenges and constraints}
    AVs are the future of private and public transports. This is a new research field and a lot of work as to be done especially in the security field. As we will see in the following sections many cyber attacks can be done by using sensors or communication channel leaks. 
    A lot of work as to be done also in the image analysis and computational power instead to perform always the best decision at the right time.
