\section{Open issues, challenges and future reserch direction}
    AV development is an emerging area, and most of information on AVs is confidential. Furthermore, there are no international standards for AV development, safety, and security available yet.
    This makes the research into AV safety and security extremely difficult.
    \newline
    Alongside the development of AVs, more personal devices and infrastructures will be introduced into the AV network, which potentially will expose AVs to more vulnerabilities. The following are several open issues, which should be addressed in the future.
    \begin{itemize}
        \item Ensuring V2X communication security is extremely important, because attacks on AVs could spread to smart infrastructures and vice versa. For example, an attack on electric vehicle could spread to the power grid infrastructure through the electric charging equipment up to the utility system. Developing secure communications and defense mechanisms are examples of future research in this area;
        
        \item Safety and security countermeasure consistency Vehicle safety analysis and security analysis are often performed separately, consequently, safety and security countermeasures are designed and developed independently. There is a need of future research into the inter-relationships and consistency between AV safety and security countermeasures;
        
        \item Safe and secure mixed traffic systems on public roads, AVs need to interact and cooperate with other automated and non-automated road users, such as regular vehicles, cyclists, and pedestrians, in order to reach an agreement about safe future motion plans. Future research into safe and secure integration of AVs into mixed traffic environments and human-AV interaction is urgently needed;
        
        \item A lot of work has to be done also to make secure the trasmission of data, provided by sensors, through CAN bus. If no security tool will be put on the CAN bus, like encryption, mission planning data will never be safe from tampering.
    \end{itemize}